### 2019-03-12 papers/journal/synth-dia.tex
Minor update on dia

	\begin{tikzpicture}[->,>=stealth', auto , node distance=3.1cm,
	  thick,main node/.style={rectangle,draw}]
	 % 	\begin{scope}[]
	  \node[main node, text width=1.5cm] (pm) {PM { \^{Qa5} 
	  		                     \^{Qa7} \^{Qbc2} \^{Qbc7}}};
	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {EE { \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {LE { \^{Qa8} \^{Qb8} \^{Qc8}}};

@@

	  %pm <-> ee
	  \path (ee) edge[bend left=32] node [below, rotate=-15] {\^{R3}} (pm);
	  \path (pm) edge[bend left=30, text width=2.0cm] node [above,rotate=-45] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
	\end{tikzpicture}
  \end{subfigure}%
 % \end{scope}
%  \vspace{1.2cm}
  \begin{subfigure}[b]{0.49\linewidth}
	  \begin{tikzpicture}[->,>=stealth',auto,node distance=3.5cm,
	  thick,main node/.style={rectangle,draw}]
	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
	  \node[main node,text width=1.5cm] (pm) {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7 ...}}};
	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {EE {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3} ... }};
	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8 ...}}};

>>>>

	\begin{tikzpicture}[->,>=stealth', auto , node distance=3.1cm,
	  thick,main node/.style={rectangle,draw}]
	 % 	\begin{scope}[]
	  \node[main node, text width=1.5cm] (pm) {\textbf{PM:} { \^{Qa5} 
	  		                     \^{Qa7} \^{Qbc2} \^{Qbc7}}};
	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} { \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {\textbf{LE:} { \^{Qa8} \^{Qb8} \^{Qc8}}};

@@

	  %pm <-> ee
	  \path (ee) edge[bend left=32] node [below, rotate=-15] {\^{R3}} (pm);
	  \path (pm) edge[bend left=30, text width=2.0cm] node [above,rotate=-45] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
	\end{tikzpicture}
  \end{subfigure}%
 % \end{scope}
%  \vspace{1.2cm}
  \begin{subfigure}[b]{0.49\linewidth}
	  \begin{tikzpicture}[->,>=stealth',auto,node distance=3.5cm,
	  thick,main node/.style={rectangle,draw}]
	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
	  \node[main node,text width=1.5cm] (pm) {\textbf{PM:} {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7 ...}}};
	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3} ... }};
	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {\textbf{LE:} {\small \^{Qa8} \^{Qb8} \^{Qc8 ...}}};
